---
title: "Title: template"
subtitle: "Astrid Thébault Guiochon, ..., Hakim Djeriouat </br><i>Study of Cognitive Mechanisms (EMC) Laboratory</i>"
# ─── Authors ───
authors: 
  - name: Astrid Thébault Guiochon
    email: a.thebaultguiochon@univ-lyon2.fr
    orcid: 0009-0007-8941-0143
    url: https://emc.univ-lyon2.fr/equipes/neurocognition-criminalite-ncc/thebault-guiochon-astrid
# ─── Format ───
format: 
 html:
# ─── Theme ───
    highlight-style: github
    theme:
      light: "themes/as.scss"
      dark: "themes/as-dark.scss"
    # ─── Sections ───
    number-sections: true
    number-depth: 3
    # ─── Table of contents ───
    toc: true
    toc_float: true
    # ─── Output ───
    embed-resources: true
    code-fold: true
    # ─── Figures ───
    fig-align: "center"
    fig-cap-location: "top"
    tbl-theme: "center"
    # ─── Banner ───
    title-block-banner: "#B7A0CD"
# ─── Dark mode ───
lightbox: true
# ─── Informations ───
date-modified: last-modified
date-format: long
# ─── Execution ───
execute: 
  message: false
  warning: false
execute-dir: project 
output-dir: _outputs
# ─── Bibliography ───
bibliography: 
  - "references/references.bib"
  - "references/packages.bib"
nocite: |
  @*
csl: 
  "references/apa.csl"
---

::: callout-note
### Description

In this study, we aim to ..
:::

# Setup

## Packages

```{r}
#| label: setup
#| code-summary: Packages
#| code-fold: true
#| output: false 

# ─── Correlation Matrix ───

if (!require("correlation")) {
    install.packages("correlation")
}
library(correlation)            
# ─── Data Manipulation ───
if (!require("dplyr")) {
    install.packages("dplyr")
}
library(dplyr)                  

# ─── JS Data Table ───
if (!require("DT")) {
    install.packages("DT")
}
library(DT)

# ─── Plotting ───
if (!require("ggplot2")) {
    install.packages("ggplot2")
}
library(ggplot2) 
source("./themes/improper-prior-ggtheme.R")

# ─── Rendering ───
if (!require("knitr")) {
    install.packages("knitr")
}
library(knitr)

# ─── Label Data ───
if (!require("labelled")) {
    install.packages("labelled")
}

# ─── 3D Data Visualization ───
if (!require("rgl")) {
    install.packages("rgl")
}
library(rgl) 
knitr::knit_hooks$set(webgl = hook_webgl)

# ─── Dataframes Manipulation ───
if (!require("tibble")) {
    install.packages("tibble")
}
library(tibble) 

# ─── Data Tidying ───
if (!require("tidyr")) {
    install.packages("tidyr")
}
library(tidyr) 

# ─── Data Manipulation ───
# Includes ggplot2, dplyr, tidyr, readr, tibble, stringr, forcats
# if (!require("tidyverse")) {
#     install.packages("tidyverse")
# }
# library(tidyverse)
```

## References

```{r}
#| label: refs
#| code-summary: "References"
#| code-fold: true 
#| output: false 

knitr::write_bib(c(.packages()), 
                 file = "references/packages.bib")
```

# Project

## Preregistration

### Study Information

#### Hypotheses

### Design Plan

#### Study Type

Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.

#### Binding

No blinding is involved in this study.

#### Is there any additional blinding in this study?

/

#### Study design


#### Stimuli validation

/

#### Randomization

### Sampling Plan

#### Existing Data

Registration prior to creation of data.

#### Explanation of existing data

/

#### Data collection procedures


#### Sample size

#### Sample size rationale

#### Stopping rule

### Variables

#### Manipulated variables

#### Measured variables

#### Indices

/

### Analysis Plan

#### Statistical models

#### Transformation

#### Inference criteria

/

#### Data exclusion

Participants flagged as fraudulent respondents, who do not complete the task or who failed manipulation checks will be excluded from our analyses. Participants who present aberrant response time (± 2.5 SD mean) all along the experiment will also be treated as outliers, and excluded from analyses.

#### Missing data

Participants with missing data will be excluded from analyses.

#### Exploratory analysis

### Other

#### Other

#### References

See the references section for the full list of references used in this document. 
